---
title: "Superstore data analysis"
author: "Aaron Silberman"
date: "`r Sys.Date()`"
output: 
  rmarkdown::github_document
runtime: shiny
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
library(pacman)
p_load(tidyverse,janitor,lubridate,ggrepel,highcharter,tinytex)
options(tinytex.verbose = TRUE)
comma <- function(x) format(x, digits = 2, big.mark = ",")
```

## Introduction

This is an exploratory and descriptive analysis of this Superstore's
customers, products, segments, and regions to better understand what and
who to target or avoid in future campaigns, thereby providing
data-driven insights.

Based on the dataset, we will be attempting to answer the following, but
also will answer more questions as they arise through analysis:

1.  Which products are the best selling? Least selling?

    -   Which products are the most profitable? Least profitable?

2.  What product (sub)categories have the highest sales? Lowest sales?

    -   Which product (sub)categories are the most profitable? Least
        profitable?

3.  What is the composition of the customer base?

    -   By segment?

    -   By region?

## Cleaning and processing data

First, I'll import the data and get acquainted. I'll remove names from
the imported file to preserve data anonymity.

```{r}
Superstore_data <- read_csv("~/Downloads/Sample - Superstore 2.csv") %>% 
  clean_names() %>% 
  select(-c(7)) %>% 
  mutate(order_date = as.Date(order_date, format = "%m/%d/%y"),
         ship_date = as.Date(ship_date, format = "%m/%d/%y"))
skimr::skim(Superstore_data) 
```

As we can see from the skim, each variable has a complete rate of 1, so
we can move on knowing that the data are complete.

Now we can check for data input errors in categorical data, including
region, segment, ship mode, category, and subcategory.

```{r}
unique(Superstore_data$segment)
unique(Superstore_data$ship_mode)
unique(Superstore_data$region)
unique(Superstore_data$category)
unique(Superstore_data$sub_category)
```

The data looks to be free of input errors, so we can move on.

### Variable Generation

Now that the data is clean, now we'll create some variables. First,
we'll create a turnaround time variable to calculate the amount of days
between the order date and ship date.

```{r}
Superstore_data <- Superstore_data%>% 
  mutate(order_date = as.Date(order_date, format = "%m/%d/%y"),
         ship_date = as.Date(ship_date, format = "%m/%d/%y"),
         turnaround = ship_date - order_date)
Superstore_data %>% 
  select(order_date, ship_date, turnaround) %>% 
  head() %>% 
  DT::datatable()
```

Next, we'll create a profit margin variable for each product to better
compare profitability across products and categories.

```{r}
Superstore_data <- Superstore_data %>% 
  mutate(margin = round(profit/sales, 2))
Superstore_data %>% 
  select(sales, profit, margin) %>% 
  head() %>% 
  DT::datatable()
```

## Analysis

### Sales, Profits, and Margins

First we'll see which segments, regions, categories, and subcategories
are have the greatest sales values and are most profitable.

#### Segments

```{r}
agg_by_segment <- aggregate(cbind(sales, profit) ~ segment, data = Superstore_data, sum)
agg_by_segment <- agg_by_segment[order(agg_by_segment$profit, decreasing = T),] %>% 
  mutate(sales = round(sales,2),
         profit = round(profit,2)) 
DT::datatable(agg_by_segment, caption = "Total sales and profits for each customer segment ($)")
```

```{r}
Superstore_data %>% 
  group_by(segment) %>% 
  summarise(value = sum(sales)) %>% 
  mutate(value = value/sum(value, na.rm = T)*100) %>% 
  mutate(value = round(value)) %>% 
  arrange(-value) %>% 
  hchart("pie",hcaes(x=segment,y=value, color=segment), name=" sales proportion%",dataLabels=list(enabled=TRUE,format="{point.name}: {point.y}%"))
```

```{r}
Superstore_data %>% 
  group_by(segment, category) %>% 
  summarise(n=sum(sales)) %>% 
  ggplot(aes(x=segment, y = category, fill = n)) +
  scale_fill_distiller(direction = 1) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste(round(n,2))), color = "black", size = 4)+
  labs(title = "Sales by customer segment and product category", 
       x = "Segment", 
       y = "Category", 
       fill = "Sales ($)" )
```

```{r}
Superstore_data %>% 
  group_by(segment, sub_category) %>% 
  summarise(n=sum(sales)) %>% 
  ggplot(aes(x=segment, y = sub_category, fill = n)) +
  scale_fill_distiller(direction = 1) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste(round(n,2))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Sales by customer segment and product subcategory",
       y = "Subcategory",
       x = "Segment",
       fill = "Sales ($)")
```

```{r}
Superstore_data %>% 
  group_by(segment, category) %>% 
  summarise(n=sum(profit)) %>% 
  ggplot(aes(x=segment, y = category, fill = n)) +
  scale_fill_distiller(direction = 1) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste(round(n,0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Profits by customer segment and product category",
       x= "Segment",
       y = "Category",
       fill = "Profits ($)")
```

```{r}
Superstore_data %>% 
  group_by(segment, category) %>% 
  summarise(n=mean(profit)) %>% 
  ggplot(aes(x = segment, y = category, fill = n)) +
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Sales by customer segment and product category",
       x = "Segment",
       y = "Category",
       fill = "Profit ($)")
```

```{r}
Superstore_data %>% 
  group_by(segment, sub_category) %>% 
  summarise(n=sum(profit)) %>% 
  ggplot(aes(x=segment, y = sub_category, fill = n)) +
  scale_fill_distiller(direction = 1) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste(round(n,0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Profits by customer segment and product subcategory",
       x= "Segment",
       y = "Subcategory",
       fill = "Profits ($)")
```

```{r}
Superstore_data %>% 
  group_by(segment, sub_category) %>% 
  summarise(n=mean(profit)) %>% 
  ggplot(aes(x=segment, y = sub_category, fill = n)) +
  scale_fill_distiller(direction = 1) +
  geom_tile() +
  geom_text(aes(label = paste(round(n,0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Aveage Profits by customer segment and product subcategory",
       x= "Segment",
       y = "Subcategory",
       fill = "Average Profits ($)")
```

```{r}
Superstore_data %>% 
  group_by(segment, region) %>% 
  summarise(n=sum(sales)) %>% 
  ggplot(aes(x = segment, y = region, fill = n)) +
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Sales by customer segment and region",
       x = "Segment",
       y = "Region",
       fill = "Sales ($)")
```

```{r}
Superstore_data %>% 
  group_by(segment, region) %>% 
  summarise(n=sum(profit)) %>% 
  ggplot(aes(x = segment, y = region, fill = n)) +
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Profit by customer region and product category",
       x = "Segment",
       y = "Region",
       fill = "Profit ($)")
```

##### Observations:

-   Most sales are to consumers in the East and West regions. Consumers
    in the West were by far the most profitable, while home office
    customers in the South were the least.

    -   On average, however, home office customers' technology purchases
        are the most profitable.

-   On average, selling copiers is by far the most profitable good sold
    across each segment, whereas selling tables nets losses across each
    segment.

-   The technology category has the greatest value of sales and profits
    across segments, whereas furniture tends to sell the least.

-   Phones and chairs have the highest value of sales in each segment,
    and fasteners are the poorest performing.

-   Phones and copiers are the most profitable in the Consumer segment,
    while Tables and Bookcases tend to lose money.

#### Regions

```{r}
agg_by_region <- aggregate(cbind(sales, profit) ~ region, data = Superstore_data, sum)
agg_by_region <- agg_by_region[order(agg_by_region$profit, decreasing = T),] %>% 
  mutate(sales = round(sales,2),
         profit = round(profit, 2))
DT::datatable(agg_by_region)
```

```{r}
Superstore_data %>% 
  group_by(region) %>% 
  summarise(value = sum(sales)) %>% 
  mutate(value = value/sum(value, na.rm = T)*100) %>% 
  mutate(value = round(value)) %>% 
  arrange(-value) %>% 
  hchart("pie",hcaes(x=region,y=value, color=region), name=" sales proportion%",dataLabels=list(enabled=TRUE,format="{point.name}: {point.y}%"))
```

As we can see, customers are pretty evenly distributed across each
region, but sales tend to be best in the West and East regions.

```{r}
Superstore_data %>% 
  group_by(region, category) %>% 
  summarise(n=sum(sales)) %>% 
  ggplot(aes(x = region, y = category, fill = n)) +
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Sales by customer region and product category",
       x = "Region",
       y = "Category",
       fill = "Sales ($)")
```

Technology is the best seller across across each region except the West,
where furniture is the best seller. Furniture sells worst in the South.

```{r}
Superstore_data %>% 
  group_by(region, category) %>% 
  summarise(n=sum(profit)) %>% 
  ggplot(aes(x = region, y = category, fill = n)) +
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Profits by customer region and product category",
       x = "Region",
       y = "Category",
       fill = "Profit ($)")
```

Office supplies in the West region are the most profitable, whereas
furniture in the Central region net the Superstore a loss.

```{r}
Superstore_data %>% 
  group_by(region, category) %>% 
  summarise(n=mean(profit)) %>% 
  ggplot(aes(x = region, y = category, fill = n)) +
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Average profit by customer region and product category",
       x = "Region",
       y = "Category",
       fill = "Average Profit ($)")
```

Technology is, on average, the most profitable category of goods sold,
while furniture is much less profitable.

```{r}
Superstore_data %>% 
  group_by(region, sub_category) %>% 
  summarise(n=sum(sales)) %>% 
  ggplot(aes(x = region, y = sub_category, fill = n))+
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n,0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Sales by customer region and product subcategory",
       x = "Region",
       y = "Subcategory",
       fill = "Sales ($)")
```

Sales for chairs in each region tend to do best, whereas sales for
fasteners tend not to do well.

```{r}
Superstore_data %>% 
  group_by(region, sub_category) %>% 
  summarise(n=sum(profit)) %>% 
  ggplot(aes(x = region, y = sub_category, fill = n)) +
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Profits by customer region and product subcategory",
       x = "Region",
       y = "Category",
       fill = "Profits ($)")
```

Interestingly, tables lose money in each region except the West.
Copiers, Phones, and Chairs are the most profitable products.

```{r}
Superstore_data %>% 
  group_by(region, sub_category) %>% 
  summarise(n=mean(profit)) %>% 
  ggplot(aes(x = region, y = sub_category, fill = n)) +
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  theme_bw()+
  labs(title = "Average profits by customer region and product category",
       x = "Region",
       y = "Subcategory",
       fill = "Average Profit ($)")
```

On average, copiers are the most profitable good sold across each
region. Machines are only profitable in the East, and net losses in each
other region.

##### Observations:

-   Most sales and profits are in the East and West.

-   Technology, mostly phones, tend to outperform other product
    categories and subcategories.

-   Copiers are the most profitable, on average, across each region.
    Tables tend to yield losses in each region.

### Sales vs Profits

```{r}
Superstore_data %>% 
  ggplot(aes(x = sales, y = profit)) +
  geom_jitter()+
  geom_hline(yintercept = 0, color = "red")+
  theme_bw()+
  labs(title = "Sales vs Profits",
       x = "Sales",
       y = "Profits")
```

There is generally a positive relationship between sales and profits,
though the relationship tends to hover around a minor, positive
relationship.

### Discounts

To see the impact of discounts on sales and profits, we'll cut the
Discount variable into ranges.

```{r}
Superstore_data<- Superstore_data %>% 
  mutate(discount = cut_width(discount, 0.1, boundary = 0))
```

Now that the discount variable has been broken down, we'll see its
impact on each category and subcategory.

#### Technology

```{r}
Superstore_data %>% 
  filter(category == "Technology") %>% 
  ggplot(aes(x = sales, y = profit, color = discount))+
  geom_point()+
  geom_hline(yintercept = 0, color = "red")+
  scale_x_continuous("Sales", labels = scales::dollar)+
  scale_y_continuous("Profits", labels = scales::dollar)+
  labs(title = "Technology: Sales vs Profits by product subcategory",
       color = "Discount rate",
       x = "Sales",
       y = "Profit")+
  theme(axis.text.x = element_text(angle = 45))+
  facet_wrap(~ sub_category)
```

Copiers, accessories, and phones tend to have a positive sales-profit
ratio, regardless of the discount offered. However, when the discount
offered on machines is greater than 45%, there is a negative
relationship between sales and profits.

#### Office Supplies

```{r}
Superstore_data %>% 
  filter(category == "Office Supplies") %>% 
  ggplot(aes(x = sales, y = profit, color = discount))+
  geom_point()+
  geom_hline(yintercept = 0, color = "red")+
  scale_x_continuous("Sales", labels = scales::dollar)+
  scale_y_continuous("Profits", labels = scales::dollar)+
  labs(title = "Office Supplies: Sales vs Profits by product subcategory",
       color = "Discount rate",
       x = "Sales",
       y = "Profit")+
  theme(axis.text.x = element_text(angle = 45))+
  facet_wrap(~ sub_category)
```

When the discount offered stays at or below 30%, the sales-profit ratio
stays positive. Binders are the most sensitive to discounts.

#### Furniture

```{r}
Superstore_data %>% 
  filter(category == "Furniture") %>% 
  ggplot(aes(x = sales, y = profit, color = discount))+
  geom_point()+
  geom_hline(yintercept = 0, color = "red")+
  scale_x_continuous("Sales", labels = scales::dollar)+
  scale_y_continuous("Profits", labels = scales::dollar)+
  labs(title = "Furniture: Sales vs Profits by product subcategory",
       color = "Discount rate",
       x = "Sales",
       y = "Profits")+
  theme(axis.text.x = element_text(angle = 45))+
  facet_wrap(~ sub_category)
```

Furniture tends to retain a positive sales-profit ratio only if the
discount offered to customers is no more than 15%.

#### Discounts vs Profits

Now we'll look at how discounts affect profits across each product
subcategory.

```{r}
margins <- Superstore_data %>% 
  group_by(sub_category, discount) %>% 
  summarise(n= sum(mean(profit))) %>% 
  spread(discount, n, NA)
profit_margins <- margins 
for (i in 3:7) {
  profit_margins[,i-1] = (margins[,i]-abs(margins[,i-1]))/abs(margins[,i-1])
}
DT::datatable(profit_margins)
```

```{r}
Superstore_data%>%
  group_by(sub_category, discount) %>% 
  summarise(n= sum(mean(profit))) %>% 
  ggplot(aes(x = discount, y = n))+
  geom_point(stat = "identity", show.legend = F)+
  geom_line(aes(group = sub_category))+
  geom_hline(yintercept = 0, color = "red")+
  scale_y_continuous("Profits", labels = scales::dollar)+
  facet_wrap(~sub_category, ncol = 3)+
  labs(title = "Discount vs Profit change across product sub-categories",
       x = "Discount offered")+
  theme(axis.text.x = element_text(angle = 90))
```

```{r}
Superstore_data%>%
  group_by(sub_category, discount) %>% 
  summarise(n= (mean(margin))) %>% 
  ggplot(aes(x = discount, y = n))+
  geom_point(stat = "identity", show.legend = F)+
  geom_line(aes(group = sub_category))+
  geom_hline(yintercept = 0, color = "red")+
  scale_y_continuous("Profit Margin", labels = scales::percent)+
  facet_wrap(~sub_category, ncol = 3)+
  labs(title = "Discount vs Profit Margin change across product sub-categories",
       x = "Discount offered",
       color = "Product Subcategory")+
  theme(axis.text.x = element_text(angle = 90))
```

##### Observation:

-   The margins of supplies were most greatly affected in the 0-15%
    discount range. Margins tend to worsen as the discount offered
    increases.
-   The profits of copiers and machines are most sensitive to discount
    increases.
-   Profit margins significantly decrease as discount rates increase.
    Binders, appliances, and bookcases see the largest decreases in
    profit margin.

### Time of year

Now we'll investigate whether the month of customers' orders affect
sales, profits, and margins.

```{r}
Superstore_data<- Superstore_data %>% 
  mutate(month = month(order_date, label = T))
```

```{r}
agg_by_month <- aggregate(cbind(sales, profit) ~ month, data = Superstore_data, sum)
agg_by_month <- agg_by_month[order(agg_by_month$profit, decreasing = T),] %>% 
  mutate(sales = round(sales, 2),
         profit = round(profit, 2))
DT::datatable(agg_by_month)
```

#### Category

```{r}
Superstore_data %>% 
  group_by(month, category) %>% 
  summarise(n = sum(sales)) %>% 
  ggplot(aes(x = category, y = month, fill = n))+
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  labs(title = "Sales totals per month by Product Category",
       x = "Category",
       y = "Month",
       fill = "Sales ($)")
```

```{r}
Superstore_data %>% 
  group_by(month, category) %>% 
  summarise(n = sum(profit)) %>% 
  ggplot(aes(x = category, y = month, fill = n))+
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  labs(title = "Profit totals per month by Product Category",
       x = "Category",
       y = "Month",
       fill = "Profit ($)")
```

```{r}
Superstore_data %>% 
  group_by(month, category) %>% 
  summarise(n = mean(profit)) %>% 
  ggplot(aes(x = category, y = month, fill = n))+
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  labs(title = "Average Profit per month by Product Category",
       x = "Category",
       y = "Month",
       fill = "Average Profit ($)")
```

##### Observations:

-   Sales for technology in November and furniture in December are
    highest, while furniture sales are lowest in February.

-   Items tend to become more profitable as the year progresses, likely
    due to customers saving money after the holiday season.

    -   Technology profits soared in March and October

#### Region

```{r}
Superstore_data %>% 
  group_by(month, region) %>% 
  summarise(n = sum(sales)) %>% 
  ggplot(aes(x = region, y = month, fill = n))+
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  labs(title = "Sales totals per month by Region",
       x = "Region",
       y = "Month",
       fill = "Sales ($)")
```

```{r}
Superstore_data %>% 
  group_by(month, region) %>% 
  summarise(n = sum(profit)) %>% 
  ggplot(aes(x = region, y = month, fill = n))+
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  labs(title = "Profit totals per month by Region",
       x = "Region",
       y = "Month",
       fill = "Profit ($)")
```

```{r}
Superstore_data %>% 
  group_by(month, region) %>% 
  summarise(n = mean(profit)) %>% 
  ggplot(aes(x = region, y = month, fill = n))+
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  labs(title = "Average Profits per month by Region",
       x = "Region",
       y = "Month",
       fill = "Average Profit ($)")
```

##### Observations:

-   November in the East outsells all regions in each month. February in
    the Central region is the most under-performing.

-   March in the West and November in the East are the most profitable
    months across each region. July in the Central region nets a loss

-   October tends to be a profitable month in the Central and East
    regions, but not as much in the South or West. March in the South is
    the most profitable month across each region.

#### Segments

```{r}
Superstore_data %>% 
  group_by(month, segment) %>% 
  summarise(n = sum(sales)) %>% 
  ggplot(aes(x = segment, y = month, fill = n))+
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  labs(title = "Sales totals per month by Segment",
       x = "Segment",
       y = "Month",
       fill = "Sales ($)")
```

```{r}
Superstore_data %>% 
  group_by(month, segment) %>% 
  summarise(n = sum(profit)) %>% 
  ggplot(aes(x = segment, y = month, fill = n))+
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  labs(title = "Profit totals per month by Segment",
       x = "Segment",
       y = "Month",
       fill = "Profits ($)")
```

```{r}
Superstore_data %>% 
  group_by(month, segment) %>% 
  summarise(n = mean(profit)) %>% 
  ggplot(aes(x = segment, y = month, fill = n))+
  scale_fill_distiller(direction = 1)+
  geom_tile()+
  geom_text(aes(label = paste(round(n, 0))), color = "black", size = 4)+
  labs(title = "Average Profitss per month by Segment",
       x = "Segment",
       y = "Month",
       fill = "Average Profit ($)")
```

##### Observation:

-   Consumers out-purchase all other customer segments in September,
    November and December.

-   Total profits for consumers are best in September and December.

-   On average, home office customers are the most profitable in January
    and October, whereas they are least profitable across segments and
    months in April.

### Shipping

First we'll look at shipping mode and its associated turnaround time.

```{r}
Superstore_data %>% 
  ggplot(aes(x = reorder(ship_mode, turnaround, median), turnaround))+
  geom_boxplot()+
  scale_y_continuous()+
  labs(title = "Shipping Mode and Order Turnaround Time",
       x = "Shipping Mode",
       y = "Turnaround Time (days)")
```

Now we'll look at differences across market segments and shipping mode
preferences.

```{r}
Superstore_data %>% 
  group_by(segment) %>% 
  ggplot(aes(x = segment, fill = ship_mode))+
  geom_bar(position = 'fill')+
  coord_flip()+
  labs(title = "Market Segment vs Shipping Mode Preference",
       y = "Proportion of customer base",
       x = "Customer Segment",
       fill = "Ship mode")
```

As we can see, customers tend to opt for standard class shipping,
regardless of customer segment.

Now we'll look for differences across product subcategories and shipping
mode preferences.

```{r}
Superstore_data %>% 
  group_by(sub_category) %>% 
  ggplot(aes(x = sub_category, fill = ship_mode))+
  geom_bar(position = 'fill')+
  coord_flip()+
  labs(title = "Product Subcategory vs Shipping Mode Preferences",
       x = "Product Subcategory",
       y = "Proportion of Products Sold",
       fill = "Ship mode")
```

Product subcategories also do not seem to affect shipping mode
preferences, as customers still predominately opt for standard class
shipping.

### Statistical and predictive analysis

```{r}
summary(lm(profit ~ discount * sub_category * sales, data = Superstore_data))
superstore_stats <- (lm(profit ~ discount * sub_category * sales, data = Superstore_data)) 
```

The interaction of discount offered, product subcategory, and sales
totals significantly predicts profits (R^2^ = 95.64).

#### Profits and Quantity Sold

We'll use the statistical analysis to make predictions about profits for
the firm

```{r}
Superstore_data <- Superstore_data %>% 
  mutate(prediction = predict(superstore_stats),
         residuals = residuals(superstore_stats))
```

```{r}
Superstore_data %>% 
  filter(sub_category != 'Copiers') %>% 
  ggplot(aes(x = quantity, y = prediction)) + 
  geom_hline(aes(yintercept = 0, color = "red"))+
  geom_smooth(formula = y~s(x, bs = "cs", k = 9), method = 'gam')+
  theme(legend.position = "")+
  scale_y_continuous("Predicted Profit", labels = scales::dollar)+
  facet_wrap(~sub_category)+
  labs(title = "Quantity sold vs Predicted Profits by product subcategory",
       x = "Quantity Sold")
```

```{r}
Superstore_data %>% 
  filter(sub_category == 'Copiers') %>% 
  ggplot(aes(x = quantity, y = prediction)) + 
  geom_hline(aes(yintercept = 0, color = "red"))+
  geom_smooth(formula = y~s(x, bs = "cs", k = 9), method = 'gam')+
  theme(legend.position = "")+
  scale_y_continuous("Predicted Profit", labels = scales::dollar)+
  labs(title = "Quantity sold vs Predicted Profits for Copiers",
       x = "Quantity Sold")
```

For most product subcategories, excluding tables, more sales predict
higher products. Copiers are by far the most profitable.

#### Discounts and predicted profits

```{r}
Superstore_data %>% 
  group_by(sub_category, discount) %>% 
  ggplot(aes(x = discount, y = prediction)) + 
  geom_hline(aes(yintercept = 0, color = "black"))+
  geom_col(aes(fill = prediction))+
  theme_bw()+
  theme(legend.position = "")+
  scale_y_continuous("Predicted Profit", labels = scales::dollar)+
  facet_wrap(~sub_category, ncol = 3)+
  labs(title = "Discount offered vs Predicted Profits by product subcategory",
       x = "Discount")+
  theme(axis.text.x = element_text(angle = 90))
```

Across product subcategories, most stay profitable until the discount
offered is greater than 15-30%.

## Conclusions and Recommendations

### Conclusions:

1.  Most sales and profits are to Consumers, and in the Eastern and
    Western Regions.

2.  Technology tends to have the best total and average sales and
    profits. Furniture tends to under-perform relative to other product
    categories.

    1.  Copiers and phones are the most profitable, and tables and
        machines tend to net losses.

3.  Most products remain profitable so long as the discount offered is
    no more than 30 percent off.

    1.  Machines see the most drastic decreases in profit margin when
        the discount offered increases.

4.  Sales and profits tend to be best across each region and segment in
    September, November, and December, likely due to back to school and
    holiday shopping.

5.  Customers prefer standard shipping to other shipping methods.

6.  Using the linear model, we can confidently predict that greater
    quantity sold will generate more profits for most product
    subcategories, aside from tables.

### Recommendations:

1.  Maintain as is for the Consumer segment, and East and West regions.
    Give customers in remaining regions and segments incentives to shop
    with 15-30% discounts to increase spending without sacrificing
    profits too much.
    1.  Keep prices and quantities as is for September, November, and
        December. Incentivize spending in other months with small
        discounts.
2.  Copiers are by far the most profitable, and become more profitable
    as more are sold, so there is minimal need for providing
    discounts. 1. Consider not selling tables anymore. The margins are
    bad and tend to lose the Superstore money.
